### 2019-06-06 manuscript.tex
Update manuscript.tex

Social norm is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10} and a key approach in comprehending and intervening the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} and analyzed \cite{DuncWand11, EffeVogt15, Hayf05,,, Youn02, }.  For example, convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.  Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}

@@

Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.  This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).  The main norm theory we tested in this paper was that women’s intention on genital cutting of their daughters was dependent on other women’s intention on cutting their daughters in their community.  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.

@@

Only women with daughters to be considered for FGC were included in 
 main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples.  We included all the women with daughters who had not genital cutting because those women presented an attitude of whether to genitally cut their daughter and represented part of the community norm in the first two models.   As a result,  there were xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

The findings support the idea that the practice of FGC is supported by social values and beliefs within the community \cite{BiccMari15}

@@

Changing social norm is a key step to changing behaviour  \cie{Bicc10}.  Changes of social norms in public health beavhiors may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.  An alternative to fgc (a complete stop or a symbolic pricking) will have to provide motivation and facilitate the change of behaviour; the behavioural change will have to be a social action (i.e., gaining recognition and public participation within community) since fgc is a social norm;  and a public commitment to change in hope for reaching a critical mass needed to dismantle the normative behaviour. (using Tostan as an example) (also see \cite{Youn15}.  Promising change are observed in changing norms \cite{EvanSnid19} (and Tostan).

>>>>

Social norm is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15} and a key approach in comprehending and intervening the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} and the FGC practice is often analyzed using social norm constructs \cite{DuncWand11, EffeVogt15, Hayf05, Youn02, } (more cite{BoylCorl010, Drol11, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm)).  For example, convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.  Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}

@@

Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} (and Bicc etc, more).  This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices (i.e., cutting daughters’s genitals).  The main norm theory we tested in this paper was that women’s intention on genital cutting of their daughters was dependent on other women’s intention on cutting their daughters in their community.  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.

@@

Only women with daughters to be considered for FGC were included in main model (the daughter model) and the mixed structure (future-daughter) model, while the future model included all the women in the samples; we included only women who had daughters yet to be considered FGC in the models to analyze intention of fgc behaviour.  All woman were included in the future model.  As a result,  there were xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

The findings support the idea that the practice of FGC is supported by social values and beliefs within the community \cite{BiccMari15}.  FGC prevalence is a strong predictor of all models and it shows that norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.

@@

Changing social norm is a key step to changing behaviour  \cie{Bicc10}.  Changes of social norms in public health beavhiors may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.  An alternative to fgc (a complete stop or a symbolic pricking) will have to provide motivation and facilitate the change of behaviour; the behavioural change will have to be a social action (i.e., gaining recognition and public participation within community) since fgc is a social norm;  and a public commitment to change in hope for reaching a critical mass needed to dismantle the normative behaviour. (using Tostan as an example) (also see \cite{Youn15}.  Promising change are observed in changing norms \cite{EvanSnid19} (and Tostan).  How to foresee a community conducive to certainty for girls without fgc?
